RDF Constraints Classification Ensuring \\ High Quality of Metadata and Data

### 2015-04-27 paper/paper7/paper7.tex
section 4

Validation environments should enable users to select which constraints to validate against depending on their individual use cases.
For some use cases, 
validating constraints of $\mathcal{CT}_{B}$ constraint types may be more important than validating constraints of $\mathcal{CT}_{S}$ or $\mathcal{CT}_{C}$ constraint types.
For other use cases,
validating $\mathcal{SL}_{2}$ constraints may be sufficient without taking $\mathcal{SL}_{1}$ and $\mathcal{SL}_{0}$ constraints into account.
\tb{refer to evaluation / what do we want to know?} 
%
%- different sets of constraints for different use cases / use case specific constraints
%
%- validation against minimal set of requirements / constraints
%
%-----

>>>>

Validation environments should enable users to select which constraints to validate against depending on their individual use cases.
For some use cases, 
validating constraints of $\mathcal{CT}_{B}$ constraint types may be more important than validating constraints of $\mathcal{CT}_{S}$ or $\mathcal{CT}_{C}$ constraint types.
For other use cases,
validating $\mathcal{SL}_{2}$ constraints may be sufficient without taking $\mathcal{SL}_{1}$ and $\mathcal{SL}_{0}$ constraints into account.
We evaluate a huge amount of metadata and data represented by multiple vocabularies to get an understanding 
(1) which sets of constraint types and 
(2) which sets of constraints (associated with particular severity levels) encompass the most/fewest violated constraints (see section \ref{evaluation}).

%
%- different sets of constraints for different use cases / use case specific constraints
%
%- validation against minimal set of requirements / constraints
%
%-----
